### 2024-06-20 manuscript.tex
Cloud occurrence figure

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{img/cloud_occurrence.pdf}
\caption{Cloud occurrence by height aggregated from the 31 voyages and one station
for observations (OBS), the ICON mode, the MERRA-2 and ERA5 reanalyses. The
total cloud fraction (CF) is shown in the legend. The ranges are from the
16$^\mathrm{th}$ to the 84$^\mathrm{th}$ percentile.}
\label{fig:cloud-occurrence}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{img/cloud_occurrence_agg.pdf}
\caption{
Cloud occurrence by height aggregated from the 31 voyages and one station for
observations (OBS), the ICON model, and the MERRA-2 and ERA5 reanalyses. The
total cloud fraction (CF) is shown in the legend. The ranges are from the
16$^\mathrm{th}$ to the 84$^\mathrm{th}$ percentile. \textbf{(a)} all conditions,
\textbf{(b)}, \textbf{(c)} cyclonic and non-cyclonic conditions as identified
by cyclone tracking, \textbf{(d)}, \textbf{(e)} stable and unstable conditions
as divided by the lower tropospheric stability criterion.
}
\label{fig:cloud-occurrence}
\end{figure}
